RFMO Initial Analysis

### 2020-06-09 Scripts/RFMO Analysis.Rmd
Re-organization of files

# Set paths depending on machine Beast (jepa88), "carmelia" or Hall1000
if(Sys.info()[7] == "jepa88"){
  Data_Path <- "Z:/JULIANO_NEYMAR/FishForVisa/"
  }
if(Sys.info()[7] == "carmelia"){
  Data_Path <- "~/GitHub/FishForVisa/Temporal_Data/"
}
if(Sys.info()[7] == "hall1000"){
  Data_Path <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/"
}

@@

# The path
path_world <- paste(Data_Path,"Spatial_Data/","RFMO","/SAU_RFMO",sep="")
# #The File
fnam_world <- "SAU_RFMO_Sept_2015.shx"
# #Load it!
# 
RFMOs_sf <- st_read(dsn = path_world,
                      layer =file_path_sans_ext(fnam_world)) %>% 
  dplyr::rename(Name = RFMO_nm_s) %>% 
  st_set_crs(3832) %>% # Making sure is same proyection
  st_transform(3832) # to match shapefiles

@@

IPHC <- RFMOs_sf %>% 
  filter(Name == "IPHC") %>% 
  st_simplify(1)

ggplot(IPHC) +
  geom_sf()

>>>>

# Set paths depending on machine Beast (jepa88), "carmelia" or Hall1000
if(Sys.info()[7] == "jepa88"){
  Data_Path <- "Z:/JULIANO_NEYMAR/FishForVisa/"
  }
if(Sys.info()[7] == "carmelia"){
  Data_Path <- paste(here::here(),"/Temporal_Data", sep ="")
}
if(Sys.info()[7] == "hall1000"){
  Data_Path <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/"
}

@@

# The path
path_world <- paste(Data_Path,"/Spatial_Data/","RFMO","/SAU_RFMO",sep="")
# #The File
fnam_world <- "SAU_RFMO_Sept_2015.shx"
# #Load it!
# 
RFMOs_sf <- st_read(dsn = path_world,
                      layer =file_path_sans_ext(fnam_world)) %>% 
  dplyr::rename(Name = RFMO_nm_s) %>% 
  st_set_crs(3832) %>% # Making sure is same proyection
  st_transform(3832) # to match shapefiles

@@

IPHC <- RFMOs_sf %>% 
  filter(Name == "IPHC") %>% 
  st_simplify(preserveTopology = TRUE, dTolerance = 100)

ggplot(IPHC) +
  geom_sf() +
  facet_wrap(~OBJECTID)

head(IPHC)

Test <- RFMOs_sf %>% 
  group_by(OBJECTID, Name) %>% 
  st_combine()

ggplot(Test) +
  geom_sf()
